Group 9 Presentation

### 2021-12-05 presentation.Rmd
adding KNN model and fixing which model belongs to who

library(ISLR)
library(leaps)
library(tidyr)
library(ggplot2)
library(glmnet)
library(caret)
library(pls) 
library(tree)
library(randomForest)
library(knitr)

@@

Jorie's RF

@@

Henrique's Boosting

@@

## PLS

@@

pls_fit <- plsr(HeartDisease ~ ., data = train, type= "class", scale = TRUE, validation = "CV")
#validationplot(pls_fit, val.type = "MSEP")

pls_prediction <- predict(pls_fit, test,  ncomp = 7)
#pls_MSE <- mean((test[, "HeartDisease"] - data.frame(pls_prediction))^2)

#Confusion Matrix prep
predicted_pls <- predict(pls_fit, newdata = test)
predicted_pls <- ifelse(predicted_pls>0.5,1,0)
#confm_pls<-table(predicted=predicted_pls,True=test$HeartDisease)

#Over all correct:

#overall_pls <- (confm_pls[1,1]+confm_pls[2,2])/sum(confm_pls)

m0 <- pcr(HeartDisease~.,data =train, scale = TRUE, validation = "CV")
mse <- MSEP(m0)

m_pls <- mse$comps[which.min(as.data.frame(mse$val)[1,])]

#values to use:
#mse
#m_pls

#kable(confm_pls) #confusion matrix
#overall_pls #over all correct

>>>>

library(ISLR)
library(leaps)
library(tidyr)
library(ggplot2)
library(glmnet)
library(caret)
library(pls) 
library(tree)
library(randomForest)
library(knitr)
library(class)
library(fastDummies)

@@

Henrique's RF

@@

Jories's Boosting

@@

## KNN

@@

temp_train <- dummy_cols(train, select_columns = c("Sex", "ChestPainType", "RestingECG", "ST_Slope", "ExerciseAngina") )
temp_test <- dummy_cols(test, select_columns = c("Sex", "ChestPainType", "RestingECG", "ST_Slope", "ExerciseAngina"))

drops <- c("Sex", "ChestPainType", "RestingECG", "ST_Slope", "ExerciseAngina")
temp_train <- temp_train[, !(names(temp_train) %in% drops)]
temp_test <-temp_test[, !(names(temp_test) %in% drops)]

#trainknn <- temp_train[-temp_train$HeartDisease]
#testknn <- test[-test$HeartDisease]

num_k <- seq(1:100)

my_cv <- knn.cv(temp_train, temp_train$HeartDisease, k=num_k)

knn_pred_1 <- knn(temp_train, temp_test, temp_train$HeartDisease, k=11)

confm_knn_1<-table(knn_pred_1,test$HeartDisease)

overall_knn_1 <- (confm_knn_1[1,1]+confm_knn_1[2,2])/sum(confm_knn_1)

overall_knn_1

 #confusion matrix
kable(confm_knn_1)
mean(knn_pred_1 !=test$HeartDisease)
